Modelling state-switching functional data with hidden Markov models

### 2020-11-06 Report/Sections/appendix.tex
add t_tilde

It is straightforward to simulate realizations of the coarse-scale HMM ($X$ and $Y$) given the parameters $\Gamma$ and $\theta$. We then simulate simulate $X^*_t$ for a fixed dive $t$. Since accelerometer readings are taken at 50 hertz and this model has two-second window lengths, each window contains 100 accelerometer readings. In addition, the length of each fine-scale Markov chain is $\tilde{T}^*_t = \lfloor Y_t/2 \rfloor$. Then, given the dive type $X_t = i$, dive duration $Y_t = y_t$, and the fine-scale probability transition matrix $\Gamma^{*(i)}$, it is straightforward to simulate the subdive states $\tilde{X}^*_t$. It is much more difficult to simulate the raw acceleration data $Y^*$, and we focus on this task for the remainder of this section.

Let $DFT\{Y^*_{t,t^*}\}(k)$ be denoted as $\hat{Y}^{*(k)}_{t,t^*}$ and $DFT\{Y^*_{t,t^*}\}$ be denoted as $\hat{Y}^*_{t,t^*}$ for convenience. We first simulate $\hat Y^{*(k)}_{t,t^*}$ for all subdive windows $t^* = 1,101,\ldots$, and all Fourier coefficients $k = 0,1,\ldots,99$. We then take the inverse DFT of $\hat{Y}^*_{t,t^*}$ for all subdive windows $t^* = 1,101,\ldots$ to find $Y^*$. The details of this procedure are described below:

\begin{enumerate}
    \item We begin by simulating $\hat{Y}^{*(0)}_{t,1}$ for each dive $t = 1,2,\ldots,100$:
    $$
    	(\hat{Y}^{*(0)}_{t,1}|X^*_{t,1} = i^*) \sim \mathcal{N} \left(0, \left(100\sigma_A^{*(\cdot,i^*)}\right)^2 \right),
    $$
    where $\sigma_A^{*(\cdot,1)} = 0.05s$ and $\sigma_A^{*(\cdot,2)} = 0.1s$. 
    %
    \item Next, for each dive $t$, we simulate $\hat{Y}^{*(0)}_{t,101},\enspace \hat{Y}^{*(0)}_{t,201}, \enspace \ldots ~ $ using Equation (\ref{eqn:yhat_0}) below:
    \begin{align}	
        \Big(\hat{Y}^{*(0)}_{t,t^*}|X^*_{t,t^*} = i^*,\hat{Y}^{*(0)}_{t,t^*-100}\Big) &\sim \mathcal{N} \left(\phi_A^{*(\cdot,i^*)} \hat{Y}^{*(0)}_{t,t^*-100}, \left(100\sigma_A^{*(\cdot,i^*)}\right)^2 \right), \nonumber \\
        %
        &t^* = 101,201,\ldots
    	\label{eqn:yhat_0}
    \end{align}
    where $\phi_A^{*(\cdot,1)} = 0.99$ and $\phi_A^{*(\cdot,2)} = 0.95$. After this step we have simulated the average acceleration within each two-second window for all dives (see Equation (\ref{eqn:avg_val}) below).
    %
    \item We then simulate Fourier coefficients 1 through 49 within each window:
    \begin{equation}
        \hat{Y}^{*(k)}_{t,t^*} = a_{t,t^*}^{(k)} i\sqrt{b^{(k)}_{t,t^*}}, \quad k = 1,\ldots,49;
        \label{eqn:abYhat}
    \end{equation}
    where $a^{(k)}_{t,t^*}$ is equal to either 1 or -1, each with probability 1/2. In addition, $b^{(k)}_{t,t^*}$ has the following distribution:
    \begin{align}
    \begin{split}
    	(b^{(k)}_{t,t^*}|X^*_{t,t^*} = 1) &\sim {\rm{Gamma}}(5/k^2, 1) \\
    	%
    	(b^{(k)}_{t,t^*}|X^*_{t,t^*} = 2) &\sim \left\{\begin{array}{lr}
    	{\rm{Gamma}}(250,1), & k = 1 \\
    	{\rm{Gamma}}(50,1), & k = 2 \\
    	{\rm{Gamma}}(5/k^2, 1), \quad & k \notin \{1,2\}.
    	\end{array}\right. 
    \end{split}
    \label{eqn:bdist}
    \end{align}
    The first argument of ${\rm{Gamma}}\left(\cdot,\cdot\right)$ is the scale parameter and the second is the shape parameter. It is important that $\mathbb{E}\left(|b^{(k)}_{t,t^*}|\right)$ is proportional to $1/k^2$, as smaller expected values for larger Fourier coefficients ``smooths out" the raw acceleration data.
    %
    \item We set Fourier coefficients 50 through 99 strategically to ensure that the inverse DFT is real-valued:
    $$
    \hat{Y}^{*(50)}_{t,t^*} = 0; \qquad
	\hat{Y}^{*(k)}_{t,t^*} = -\hat{Y}^{*(100-k)}_{t,t^*} \enspace \text{for} \enspace k = 51,\ldots,99.
    $$
    %
    \item Finally, for each dive $t = 1,2,\ldots,100$ and each window $t^*=1,101,\ldots$, the raw acceleration data $\left\{Y^*_{t,t^*},\ldots,Y^*_{t,t^*+99}\right\}$ is set using the inverse discrete Fourier transform of $\hat{Y}^*_{t,t^*}$:
    %
    $$Y^*_{t,t^*+n} = IDFT\left\{\hat{Y}^*_{t,t^*}\right\}(n); \quad n = 0,\ldots,99; \quad t^* = 1,101,\ldots$$
\end{enumerate}

We now show that this construction of $Y^*$ results in the correct distributions as listed in Section \ref{subsec:data_simulation}. First, note that $\hat{Y}^{(0)}_{t,t^*}$ is just the sum of the raw acceleration values within the corresponding window:
%
\begin{align}
    \hat{Y}^{(0)}_{t,t^*} = DFT\{Y^*_{t,t^*}\}(0) &= \sum_{n=0}^{99} Y^*_{t,t^*+n} \exp\left(-\frac{i2\pi}{99}*0*n\right) \nonumber \\
    &= \sum_{n=0}^{99} Y^*_{t,t^*+n} \nonumber \\
    &= 100A^*_{t,t^*}.
    \label{eqn:avg_val}
\end{align}
%
Combining Equation (\ref{eqn:avg_val}) above with Equation (\ref{eqn:yhat_0}) gives the distribution of $\Zone_{t,t^*}$: 
%
$$\left(100\Zone_{t,t^*} | X^*_{t,t^*} = i^*, \Zone_{t,t^*-100} \right) \sim \mathcal{N} \left(100\phi_A^{*(\cdot,i^*)} \Zone_{t,t^*-100}, \left(100\sigma_A^{*(\cdot,i^*)}\right)^2 \right)$$
%
$$\implies \left(\Zone_{t,t^*} | X^*_{t,t^*} = i^*, \Zone_{t,t^*-100} \right) \sim \mathcal{N} \left(\phi_A^{*(\cdot,i^*)} \Zone_{t,t^*-100}, \left(\sigma_A^{*(\cdot,i^*)}\right)^2 \right).$$
%
This distribution is consistent with a CarHMM with Normal emission distributions and $\mu_A^{*(\cdot,i^*)} = 0$. We also have that $\sigma_A^{*(\cdot,1)} = 0.05s$, $\phi_A^{*(\cdot,1)} = 0.99$, $\sigma_A^{*(\cdot,2)} = 0.1s$, and $\phi_A^{*(\cdot,2)} = 0.95$.

To calculate the wiggliness $\Ztwo_{t,t^*}$, we pick $\tilde{\omega} = 10$ periods per window (or 5 Hz). Recall that $\Ztwo_{t,t^*}$ is the sum of Gamma-distributed random variables with identical scale parameters, so the distribution of $\Ztwo_{t,t^*}$ is also Gamma-distributed. From Equation (\ref{eqn:abYhat}), we have:
%
\begin{equation}
    \Ztwo_{t,t^*} = \sum_{k=1}^{10} \big|\big|\hat{Y}^{(k)}_{t,t^*}\big|\big|^2 = \sum_{k=1}^{10} \big|\big|a^{(k)}_{t,t^*}i\sqrt{b^{(k)}_{t,t^*}}\big|\big|^2 = \sum_{k=1}^{10} \big|b^{(k)}_{t,t^*}\big|
    \label{eqn:Wb}
\end{equation}
%
since $a^{(k)}_{t,t^*} \in \{-1,1\}$. Combining Equation (\ref{eqn:Wb}) above with Equation block (\ref{eqn:bdist}) gives
%
$$\left(\Ztwo_{t,t^*}|X^*_{t,t^*} = 1\right) \sim {\rm{Gamma}}\left(\sum_{k=1}^{10} 5/k^2 = 10.10, 1.00 \right) \text { and }$$
%
$$\left(\Ztwo_{t,t^*}|X^*_{t,t^*} = 2\right) \sim {\rm{Gamma}}\left(300 + \sum_{k=3}^{10} 5/k^2 = 305.94 , 1.00 \right),$$
%
where the first argument of ${\rm{Gamma}}\left(\cdot,\cdot\right)$ is the scale parameter and the second is the shape parameter. Simple calculation of the mean and variance of a Gamma distribution shows that $\mu_W^{*(\cdot,1)} = 10.10$, $\sigma_W^{*(\cdot,1)} = 3.18$, $\mu_W^{*(\cdot,2)} = 305.94$, and $\sigma_W^{*(\cdot,2)} = 17.49$.

@@

The overall likelihood of the CarHHMM-DFT model is as follows:
%
$$\calL_{\text{CarHHMM-DFT}}(\theta,\theta^*,\Gamma,\Gamma^*;y,z^*) = \delta P(y_1,z_1^*;\theta,\theta^*,\Gamma^*) \prod_{t=2}^T \Gamma P(y_t,z_t^*;\theta,\theta^*,\Gamma^*) \mathbf{1}_N.$$
%
In particular,
%
\begin{align*}
P(y_t,z_t^*;\theta,\theta^*,\Gamma^*)  = \text{diag}\Big[&f^{(1)}(y_t;\theta^{(1)})\calL_{\text{CarHMM-DFT}}\left(\theta^*,\Gamma^{*(1)};z_t^*\right), \ldots , \\
&f^{(N)}(y_t;\theta^{(N)})\calL_{\text{CarHMM-DFT}}\left(\theta^*,\Gamma^{*(N)};z_t^*\right) \Big],
\end{align*}
%
where $f^{(i)}(y_t;\theta^{(i)})$ is the emission distribution of dive duration given that $X_t = i$. The likelihood $\calL_{\text{CarHMM-DFT}}$ corresponds to the fine-scale model and is equal to the following:
%
$$\calL_{\text{CarHMM-DFT}}\left(\theta^{*},\Gamma^{*(i)};z_t^*\right) = \delta^{*(i)} \prod_{z^*_{t,t^*} \in z^*_t} \Gamma^{*(i)} P(z^*_{t,t^*}|z^*_{t,t^*-100};\theta^*) \mathbf{1}_N,$$
%
where $P(z^*_{t,t^*}|z^*_{t,t^*-100};\theta^*)$ is an $N^* \times N^*$ diagonal matrix with $(i^*,i^*)^{th}$ entry equal to $f^{*(\cdot,i^*)}(z^*_{t,t^*}|z^*_{t,t^*-100}; \theta^{*(\cdot,i^*)})$.
%
Recall that $z^*_t = \left\{z^*_{t,1},z^*_{t,101},z^*_{t,201},\ldots\right\}$ and that $f^{*(\cdot,i^*)}(\cdot|z^*_{t,t^*-100}; \theta^{*(\cdot,i^*)})$ is the probability density function of $\Z_{t,t^*}$ conditioned on $X^*_{t,t^*} = i^*$ and $\Z_{t,t^*-100} = z^*_{t,t^*-100}$.

>>>>

It is straightforward to simulate realizations of the coarse-scale HMM ($X$ and $Y$) given the parameters $\Gamma$ and $\theta$. Since accelerometer readings are taken at 50 hertz and this model has two-second window lengths, each window contains 100 accelerometer readings. In addition, the length of each fine-scale Markov chain is $\tilde T ^*_t = \lfloor Y_t/2 \rfloor$. Then, given the dive type $X_t = i$, dive duration $Y_t = y_t$, and the fine-scale probability transition matrix $\Gamma^{*(i)}$, it is straightforward to simulate the subdive states $\tilde{X}^*_t$ for a particular dive $t$. It is much more difficult to simulate the raw acceleration data $Y_t^*$, and we focus on this task for the remainder of the section.

Let $DFT\{Y^*_{t,100(\tilde t^* - 1) + 1},\ldots,Y^*_{t,100\tilde t^*}\}(k)$ be denoted as $\hat{Y}^{*(k)}_{t,\tilde t^*}$ and $DFT\{Y^*_{t,100(\tilde t^* - 1) + 1},\ldots,Y^*_{t,100\tilde t^*}\}$ be denoted as $\hat{Y}^*_{t,\tilde t^*}$ for convenience. We simulate $Y_t^*$ in three steps: 1) simulate the average acceleration within each window $\left(Y^{*(0)}_{t,\tilde t^*}\right)$, 2) simulate all other Fourier coefficients within each window $\left(\hat Y^{*(k)}_{t,\tilde t^*}, k = 1,\ldots,99\right)$, and 3) take the inverse $DFT$ of $\hat{Y}^*_{t,\tilde t^*}$ to retrieve $\{Y^*_{t,100(\tilde t^* - 1) + 1},\ldots,Y^*_{t,100\tilde t^*}\}$. The details of this procedure are described below:

\begin{enumerate}
\item Simulate the average acceleration $Y^{*(0)}_{t,\tilde t^*}$ for each window $\tilde t^* = 1,2,\ldots,\tilde T^*_t$ using the following procedure:
\begin{enumerate}
    \item Simulate $\hat{Y}^{*(0)}_{t,1}$:
    $$
    	(\hat{Y}^{*(0)}_{t,1}|X^*_{t,1} = i^*) \sim \mathcal{N} \left(0, \left(100\sigma_A^{*(\cdot,i^*)}\right)^2 \right)
    $$
    where $\sigma_A^{*(\cdot,1)} = 0.05s$ and $\sigma_A^{*(\cdot,2)} = 0.1s$. 
    %
    \item Simulate $\hat{Y}^{*(0)}_{t,2}, \ldots,\enspace \hat{Y}^{*(0)}_{t,\tilde T^*_t}$ using Equation (\ref{eqn:yhat_0}) below:
    \begin{align}	
        \Big(\hat{Y}^{*(0)}_{t,\tilde t^*}|\tilde X^*_{t,\tilde t^*} = i^*,\hat{Y}^{*(0)}_{t,\tilde t^*-1}\Big) &\sim \mathcal{N} \left(\phi_A^{*(\cdot,i^*)} \hat{Y}^{*(0)}_{t,\tilde t^*-1}, \left(100\sigma_A^{*(\cdot,i^*)}\right)^2 \right), \nonumber \\
        %
        &t^* = 2,\ldots, \tilde T^*_t
    	\label{eqn:yhat_0}
    \end{align}
    where $\phi_A^{*(\cdot,1)} = 0.99$ and $\phi_A^{*(\cdot,2)} = 0.95$. 
    \end{enumerate}
    After this step we have simulated the average acceleration within each two-second window for all dives (see Equation (\ref{eqn:avg_val}) below).
    \item Simulate the other Fourier coefficients $\left(Y^{*(k)}_{t,\tilde t^*}\right)$ for each window $\tilde t^* = 1,2,\ldots,\tilde T^*_t$ and $k = 1,\ldots,99$ using the following procedure:
    \begin{enumerate}
    %
    \item Simulate Fourier coefficients 1 through 49:
    \begin{equation}
        \hat{Y}^{*(k)}_{t,\tilde t^*} = a_{t,\tilde t^*}^{(k)} i\sqrt{b^{(k)}_{t,\tilde t^*}}, \quad k = 1,\ldots,49;
        \label{eqn:abYhat}
    \end{equation}
    where $a^{(k)}_{t,\tilde t^*}$ is equal to either 1 or -1 each with probability 1/2, and $b^{(k)}_{t,\tilde t^*}$ has the following distribution:
    \begin{align}
    \begin{split}
    	(b^{(k)}_{t,\tilde t^*}|\tilde X^*_{t,\tilde t^*} = 1) &\sim {\rm{Gamma}}(5/k^2, 1) \\
    	%
    	(b^{(k)}_{t,\tilde t^*}|\tilde X^*_{t,\tilde t^*} = 2) &\sim \left\{\begin{array}{lr}
    	{\rm{Gamma}}(250,1), & k = 1 \\
    	{\rm{Gamma}}(50,1), & k = 2 \\
    	{\rm{Gamma}}(5/k^2, 1), \quad & k \notin \{1,2\}.
    	\end{array}\right. 
    \end{split}
    \label{eqn:bdist}
    \end{align}
    The first argument of ${\rm{Gamma}}\left(\cdot,\cdot\right)$ is the scale parameter and the second is the shape parameter. The magnitude of the $k^{th}$ Fourier coefficient is equal to $b^{(k)}_{t,\tilde t^*}$, which decays like $1/k^2$ to ``smooth out" the raw acceleration data.
    %
    \item Set Fourier coefficients 50 through 99 so the inverse DFT is real-valued:
    $$
    \hat{Y}^{*(50)}_{t,\tilde t^*} = 0, \qquad
	\hat{Y}^{*(k)}_{t,\tilde t^*} = -\hat{Y}^{*(100-k)}_{t,\tilde t^*} \enspace \text{for} \enspace k = 51,\ldots,99.
    $$
    \end{enumerate}
    \item Finally, set the raw acceleration data within each window $\{Y^*_{t,100(\tilde t^* - 1) + 1},\ldots,Y^*_{t,100\tilde t^*}\}$ with the inverse discrete Fourier transform of $\hat{Y}^*_{t,\tilde t^*}$:
    %
    $$\{Y^*_{t,100(\tilde t^* - 1) + 1},\ldots,Y^*_{t,100\tilde t^*}\} \equiv IDFT\left\{\hat{Y}^*_{t,\tilde t^*}\right\}$$
    for $\tilde t^* = 1,\ldots,\tilde T^*_t.$
\end{enumerate}

We now show that this construction of $Y^*_t$ results in the distributions listed in Section \ref{subsec:data_simulation}. First, note that $\hat{Y}^{(0)}_{t,\tilde t^*}$ is just the sum of the raw acceleration values within window $\tilde t$:
%
\begin{align}
    \hat{Y}^{(0)}_{t,\tilde t^*} &=
    DFT\{Y^*_{t,100(\tilde t^* - 1) + 1},\ldots,Y^*_{t,100\tilde t^*}\}(0) \nonumber \\
    &= \sum_{n=0}^{99} Y^*_{t,100(\tilde t^* - 1) + 1 + n} \exp\left(-\frac{i2\pi}{99}*0*n\right) \nonumber \\
    &= \sum_{n=1}^{100} Y^*_{t,100(\tilde t^* - 1) + n} \nonumber \\
    &= 100A^*_{t,\tilde t^*}.
    \label{eqn:avg_val}
\end{align}
%
Combining Equation (\ref{eqn:avg_val}) above with Equation (\ref{eqn:yhat_0}) gives the distribution of $\Zone_{t,\tilde t^*}$: 
%
$$\left(100\Zone_{t,\tilde t^*} | \tilde X^*_{t,\tilde t^*} = i^*, \Zone_{t,\tilde t^*-1} \right) \sim \mathcal{N} \left(100\phi_A^{*(\cdot,i^*)} \Zone_{t,\tilde t^*-1}, \left(100\sigma_A^{*(\cdot,i^*)}\right)^2 \right)$$
%
$$\implies \left(\Zone_{t,\tilde t^*} | \tilde X^*_{t,\tilde t^*} = i^*, \Zone_{t,\tilde t^*-1} \right) \sim \mathcal{N} \left(\phi_A^{*(\cdot,i^*)} \Zone_{t,\tilde t^*-1}, \left(\sigma_A^{*(\cdot,i^*)}\right)^2 \right).$$
%
This distribution is consistent with a CarHMM with Normal emission distributions and $\mu_A^{*(\cdot,1)} = \mu_A^{*(\cdot,2)} = \mu_A^{*(\cdot,i^*)} = 0$. We also have that $\sigma_A^{*(\cdot,1)} = 0.05s$, $\phi_A^{*(\cdot,1)} = 0.99$, $\sigma_A^{*(\cdot,2)} = 0.1s$, and $\phi_A^{*(\cdot,2)} = 0.95$.

To calculate the wiggliness $\Ztwo_{t,\tilde t^*}$, we pick $\tilde{\omega} = 10$ periods per window (or 5 Hz). From Equation (\ref{eqn:abYhat}):
%
\begin{equation}
    \Ztwo_{t,\tilde t^*} = \sum_{k=1}^{10} \big|\big|\hat{Y}^{(k)}_{t,\tilde t^*}\big|\big|^2 = \sum_{k=1}^{10} \big|\big|a^{(k)}_{t,\tilde t^*}i\sqrt{b^{(k)}_{t,\tilde t^*}}\big|\big|^2 = \sum_{k=1}^{10} b^{(k)}_{t,\tilde t^*}
    \label{eqn:Wb}
\end{equation}
%
since $a^{(k)}_{t,\tilde t^*} \in \{-1,1\}$ and $b^{(k)}_{t,\tilde t^*} \geq 0$. Since $\Ztwo_{t,\tilde t^*}$ is the sum of Gamma-distributed random variables with identical scale parameters, the distribution of $\Ztwo_{t,\tilde t^*}$ is also Gamma. Combining Equation (\ref{eqn:Wb}) above with Equation (\ref{eqn:bdist}) gives
%
$$\left(\Ztwo_{t,\tilde t^*}|X^*_{t,\tilde t^*} = 1\right) \sim {\rm{Gamma}}\left(\sum_{k=1}^{10} 5/k^2 = 10.10, 1.00 \right) \text { and }$$
%
$$\left(\Ztwo_{t,\tilde t^*}|X^*_{t,\tilde t^*} = 2\right) \sim {\rm{Gamma}}\left(300 + \sum_{k=3}^{10} 5/k^2 = 305.94 , 1.00 \right),$$
%
where the first argument of ${\rm{Gamma}}\left(\cdot,\cdot\right)$ is the scale parameter and the second is the shape parameter. Simple calculation of the mean and variance of a Gamma distribution reveals $\mu_W^{*(\cdot,1)} = 10.10$, $\sigma_W^{*(\cdot,1)} = 3.18$, $\mu_W^{*(\cdot,2)} = 305.94$, and $\sigma_W^{*(\cdot,2)} = 17.49$.

@@

The overall likelihood of the CarHHMM-DFT model is as follows:
%
$$\calL_{\text{CarHHMM-DFT}}(\theta,\theta^*,\Gamma,\Gamma^*;y,\z) = \delta P(y_1,\z_1;\theta,\theta^*,\Gamma^*) \prod_{t=2}^T \Gamma P(y_t,\z_t;\theta,\theta^*,\Gamma^*) \mathbf{1}_N.$$
%
In particular,
%
\begin{align*}
P(y_t,\z_t;\theta,\theta^*,\Gamma^*)  = \text{diag}\Big[&f^{(1)}(y_t;\theta^{(1)})\calL_{\text{CarHMM-DFT}}\left(\theta^*,\Gamma^{*(1)};\z_t\right), \ldots , \\
&f^{(N)}(y_t;\theta^{(N)})\calL_{\text{CarHMM-DFT}}\left(\theta^*,\Gamma^{*(N)};\z_t\right) \Big],
\end{align*}
%
where $f^{(i)}(y_t;\theta^{(i)})$ is the emission distribution of dive duration given that $X_t = i$. The likelihood $\calL_{\text{CarHMM-DFT}}$ corresponds to the fine-scale model and is equal to the following:
%
$$\calL_{\text{CarHMM-DFT}}\left(\theta^{*},\Gamma^{*(i)};\z_t\right) = \delta^{*(i)} \prod_{\tilde t^* = 2}^{\tilde T^*_t} \Gamma^{*(i)} P(\z_{t,\tilde t^*}|\z_{t,\tilde t^*-1};\theta^*) \mathbf{1}_N,$$
%
where $P(\z_{t,\tilde t^*}|\z_{t,\tilde t^*-1};\theta^*)$ is an $N^* \times N^*$ diagonal matrix with $(i^*,i^*)^{th}$ entry equal to $f^{*(\cdot,i^*)}(\z_{t,\tilde t^*}|\z_{t,\tilde t^*-1}; \theta^{*(\cdot,i^*)})$.
%
Recall that $f^{*(\cdot,i^*)}(\cdot|\z_{t,t^*-1}; \theta^{*(\cdot,i^*)})$ is the probability density function of $\Z_{t,\tilde t^*}$ when $\tilde X^*_{t,\tilde t^*} = i^*$ and $\Z_{t,\tilde t^*-1} = \z_{t,\tilde t^*-1}$.
